---
title: "Course Project"
author: "JY"
date: '2017 7 26 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Preprocessing

The training data have many "#DIV/0!", "NA", blanks, so these values need to be set to the same value of NA.
After that, some columns consists of all NA and needless columns (like X, user_names) are deleted.
"classe" is converted to factors which in needed for randomForest package.

```{r preprocessing, echo=FALSE, message=FALSE, warning=FALSE}

library(caret)
library(randomForest)

set.seed(12345)

## load data. replace "#DIV/0!", "NA"", blanks
training <- read.table("pml-training.csv", sep=",", na.strings=c("#DIV/0!","","NA"), stringsAsFactors=FALSE, header=TRUE)
testing <- read.table("pml-testing.csv", sep=",", na.strings=c("#DIV/0!","","NA"), stringsAsFactors=FALSE, header=TRUE)


##preprocessing
# omit columns with all NA's
training_data <- training[,colSums(is.na(training))==0]
testing_data <- testing[,colSums(is.na(training))==0] 

# omit unnessesary columns
training_data <- training_data[,-c(1:7)]
testing_data <- testing_data[,-c(1:7)]

# make classe factor
training_data$classe <- as.factor(training_data$classe)
```

## Modeling
Because we have a large sample size in the traing data set, devide the data into training_sub(70%) and validate_sub(30%).
Then make model with traing_sub data.

```{r modeling}
# prepair data for training and validation
inTrain <- createDataPartition(y=training_data$classe, p=0.7, list=FALSE)
training_sub <- training_data[inTrain,]
validate_sub <- training_data[-inTrain,]

## make model
model <- randomForest(classe~., data=training_sub, importance=TRUE)
```

## Evaluation

Evaluated the model with validate_sub data and confusion matrix are presented.

```{r result}
# see accuracy
result <- predict(model, validate_sub)
confusionMatrix(result, validate_sub$classe)
```

The accuracy is so high(0.9932). So, random forest is good algorithm for prediction.


## Prediction Result

In the end, the model is applied to given testing data set to predict "classe".


```{r predict}
## predict test set
predict(model, testing_data)
```

